On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-02 docs/mvfits_paper/mvf.tex
Up text describing Nagar et al. (2018) comp [15]

\par For both the $(l,m)\neq(2,2)$ \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.

@@

here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves. A residual error is also shown as an orange dashed line for the $\cw_{220}$ model presented in Ref.~\cite{Nagar:2018zoe}. This is a rational model with 14 fitted parameters compared to the polynomial model with 10 fitted parameters defined in \eqn{eq:cw_fit_1}. We observe that Ref.~\cite{Nagar:2018zoe} performs better overall while performing worse for higher $\jf$.

@@

\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting polynomial models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature. We note our comparison of $\cw_{220}$ from Ref.~\cite{Nagar:2018zoe} suggests even better fits for $(l,m,n)\neq(2,2,0)$ QNM frequencies might be achievable using a rational ansatz. We leave this extension to future modeling work.

>>>>

\par For $(l,m)\neq(2,2)$ \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.

@@

here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves. A residual error is also shown as an orange dashed line for the $\cw_{220}$ model presented in Ref.~\cite{Nagar:2018zoe}. We observe that the rational model of Ref.~\cite{Nagar:2018zoe} performs better overall while performing worse for higher $\jf$ compared to our model. While we use a polynomial ansatz, the comparison with Ref.~\cite{Nagar:2018zoe} highlights the potential of rational ansatzes.

@@

\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting polynomial models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature. We note our comparison of $\cw_{220}$ from Ref.~\cite{Nagar:2018zoe} suggests even better fits for $(l,m,n)\neq(2,2,0)$ QNM frequencies might be achievable using a rational ansatz. This is a possible avenue for future improvement.
